Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-09-26 template.tex
added analysis of logE fit, two plots of CSWs

Table \ref{tab:2} contains the preliminary results for the reconstruction of $\log_{10}E_{\rm C}$.  The results are consistent with the MC truth.  Note that when applying the change of base formula, factors of $\ln(10)$ cancel in the error ratio of Eq. \ref{eq:a_err_2}, so the error in $\log_{10} E_{\rm C}$ remains $2.0$.  The $sigma_t$ result is the average value of 15133 optimized analytic envelopes fit to signal CSWs generated by 100 PeV UHE-$\nu$ events that triggered the detector.  Note that the error in the \textit{average} $\sigma_t$ over all events fluctuates due to varying $\Delta\theta$, while the error in \textit{individual} $\sigma_t$ per CSW fit is negligible if the samples per CSW is much greater than 1.  By far, the largest sources of systematic error are \textit{reflected signals} in the CSWs.

Reflected signals are caused when more than one ray-tracing solution is available between the Askaryan radiation source and the detector.  Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that first reflect at the snow-air interface, or in the glacial firn, are known as \textit{reflected signals} \cite{}.  When \textit{direct} and \textit{reflected} signals arrive at the detector at similar times, and one or the other triggers the detector, the recorded waveforms contain direct and reflected signals.

\begin{table}
\centering
\begin{tabular}{| c | c |}
\hline
\textbf{Parameter} & \textbf{Average Value} \\ \hline
MC Truth, $E_{\rm C}$ [eV] & $10^{17}$ \\
MC Truth, $\log_{10}E_{\rm C}$ & $17$ \\
$\sigma_t$ & $1.2 \pm 0.4$ ns \\
$c_{\rm em,had}$ & 0.86 m \\
$\Delta\theta_{\rm rms}$ & 3.9 degrees \\
$E_{\rm crit}$ & 100 MeV \\
$c$ & $0.3/1.78$ m ns$^{-1}$ \\
$\sin\theta_{\rm C}$ & 0.8271 \\ \hline
\textbf{Reconstructed} $\mathbf{\log_{10}E_{\rm C}}$ & $16.5\pm 2.0$ \\
\hline
\end{tabular}
\caption{\label{tab:2} Energy reconstruction parameters used to calculate the logarithm of the UHE-$\nu$ cascade energy, $\log_{10}E_{\rm C}$.}
\end{table}

>>>>

Table \ref{tab:2} contains the preliminary results for the reconstruction of $\log_{10}E_{\rm C}$.  The results are consistent with the MC truth.  Note that when applying the change of base formula, factors of $\ln(10)$ cancel in the error ratio of Eq. \ref{eq:a_err_2}, so the error in $\log_{10} E_{\rm C}$ remains $2.0$.  The $\sigma_t$ result is the average value of optimized analytic envelopes fit to signal CSWs generated by 15133 UHE-$\nu$ events that triggered the detector with $E_{\rm C} = 100$ PeV.  Note that the error in the \textit{average} $\sigma_t$ over all events fluctuates due to varying $\Delta\theta$, while the error in \textit{individual} $\sigma_t$ per CSW fit is negligible if the samples per CSW is much greater than 1.  By far, the largest sources of systematic error are \textit{reflected signals} in the CSWs.

Reflected signals are caused when more than one ray-tracing solution is available between the Askaryan radiation source and the detector.  Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that first reflect at the snow-air interface, or in the glacial firn, are known as \textit{reflected signals}.  Complex RF signal propagation in polar ice has been studied, and even proposed as a UHE-$\nu$ energy reconstruction technique \cite{Barwick:2018497,anker2019neutrino-734}.  When \textit{direct} and \textit{reflected} signals both arrive at the detector, recorded voltage traces contain both direct and reflected signals.  The analytic envelope, however, assumes a single pulse.  Thus, direct and reflected pulses that overlap, or are closely spaced, yield larger $\sigma_t$ values than the average quoted in Tab. \ref{tab:2}.  This effect systematically overestimates the $\log_{10} E_{\rm C}$.  Two examples are shown in Fig. \ref{fig:example_waveforms}: a single-pulse CSW and a CSW containing direct and reflected signals.

\begin{table}
\centering
\begin{tabular}{| c | c |}
\hline
\textbf{Parameter} & \textbf{Average Value} \\ \hline
MC Truth, $E_{\rm C}$ [eV] & $10^{17}$ \\
MC Truth, $\log_{10}E_{\rm C}$ & $17$ \\
$c$ & $0.3/1.78$ m ns$^{-1}$ \\
$\overline{\sigma_t}$ & $1.229 \pm 0.004$ ns \\
$c_{\rm ave}$ & 0.86 m \\
$\Delta\theta_{\rm rms}$ & $3.78\pm0.04$ degrees \\
$E_{\rm crit}$ & 100 MeV \\
$\sin\theta_{\rm C}$ & 0.8271 \\ \hline
\textbf{Reconstructed} $\mathbf{\log_{10}E_{\rm C}}$ & $16.5\pm 2.0$ \\
\hline
\end{tabular}
\caption{\label{tab:2} Energy reconstruction parameters used to calculate the logarithm of the UHE-$\nu$ cascade energy, $\log_{10}E_{\rm C}$.}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{Sept25_plot1.pdf}
\includegraphics[width=0.5\textwidth]{Sept25_plot2.pdf}
\caption{\label{fig:example_waveforms} (Top) A single-pulse CSW signal (black dots) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.951$. (Bottom) A direct and reflected CSW signal (black dots and thin black line) from a 100 PeV UHE-$\nu$, matched to an analytic envelope (thick black line) with a correlation coefficient $\rho = 0.773$.}
\end{figure}
